\Large \bf Lissy: Experimenting with on-chain order books

### 2021-09-13 LaTeX-LNCS-2022/sections/paper.tex
new diagram

\begin{figure}[t]
\begin{floatrow}
\ffigbox{%
\includegraphics[width=6cm]{fig/2.png}%
}{%
  \caption{\scriptsize{\textblue{RESIZE THIS} Gas costs for enqueuing 50 random integers into five priority queue variants. For the x-axis, a value of 9 indicates it is the 9th integer entered in the priority queue. The y-axis is the cost of enqueuing in gas}. \label{fig:random_insertion}}%

@@

\multicolumn{1}{c}{} & \headrowsidebyside{\scriptsize{\shortstack{Gas Costs \\\textit{(gwei)}}}} & \headrowsidebyside{\scriptsize{Refund \textit{(gwei)} }} & \headrowsidebyside{\scriptsize{Full Refund?}} \\ \hline

@@

\end{tabular}
}{%
 \caption{\scriptsize{The gas metrics associated with dequeuing 50 integers from five priority queue variants. Full refund amount is shown but the actual refund that is applied is capped.}
\label{tab:PQUnitTests}}%
}
\end{floatrow}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\textwidth]{fig/MindMapDraft4.pdf}
\caption{\footnotesize{A design landscape for on-chain call markets.}  \label{fig:rmindmap}}
\end{figure}

>>>>

\begin{figure}[t]
\begin{floatrow}
\ffigbox{%
\includegraphics[width=6cm]{fig/2b.png}%
}{%
  \caption{\footnotesize{ Gas costs for enqueuing 50 random integers into five priority queue variants. For the x-axis, a value of 9 indicates it is the 9th integer entered in the priority queue. The y-axis is the cost of enqueuing in gas}. \label{fig:random_insertion}}%

@@

\multicolumn{1}{c}{} & \headrowsidebyside{\scriptsize{\shortstack{Gas Used}}} & \headrowsidebyside{\scriptsize{Refund}} & \headrowsidebyside{\scriptsize{Full Refund?}} \\ \hline

@@

\end{tabular}
}{%
 \caption{\footnotesize{The gas metrics associated with dequeuing 50 integers from five priority queue variants. Full refund amount is shown but the actual refund that is applied is capped.}
\label{tab:PQUnitTests}}%
}
\end{floatrow}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\textwidth]{fig/MindMapDraft5.pdf}
\caption{\footnotesize{A design landscape for on-chain call markets.}  \label{fig:rmindmap}}
\end{figure}
